Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2018-06-10 paper/galsize_paper.tex
Modified text to address minor comment 5

@@

In Figure~\ref{fig:rvir_only_clustering_absolute}, we present new measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj(\rproj).$ We measure $\wproj(\rproj)$ separately for large and small subsamples for four different $\mstar$ thresholds: an  $\mstar>10^{9.75}\msun$ sample with $z_{\rm max}=0.0435$ and $N_{\rm gal}=27658;$ an  $\mstar>10^{10.25}\msun$ sample with $z_{\rm max}=0.0663$ and $N_{\rm gal}=48571;$ 
an  $\mstar>10^{10.75}\msun$ sample with $z_{\rm max}=0.1$ and $N_{\rm gal}=52350;$ 
and an  $\mstar>10^{11}\msun$ sample with $z_{\rm max}=0.1$ and $N_{\rm gal}=33578.$ For each threshold, we split the galaxies into ``large" and ``small" subsamples, as described in \S\ref{subsec:sizedef}. As shown in Figure \ref{fig:sizedefinition}, our size-based samples  have similar stellar mass functions. Red points with jackknife-estimated error bars show SDSS measurements of $\wproj(\rproj)$ for samples of small galaxies, while blue points show the measured correlation functions for samples of large galaxies. Solid curves show $\wproj$ as predicted for these subsamples by the $\rvir-$based model of galaxy sizes described in \S\ref{subsubsec:rvirmodel}.

>>>>

We measure $\wproj(\rproj)$ separately for large and small subsamples for four different $\mstar$ thresholds: an  $\mstar>10^{9.75}\msun$ sample with $z_{\rm max}=0.0435$ and $N_{\rm gal}=27658;$ an  $\mstar>10^{10.25}\msun$ sample with $z_{\rm max}=0.0663$ and $N_{\rm gal}=48571;$ 
an  $\mstar>10^{10.75}\msun$ sample with $z_{\rm max}=0.1$ and $N_{\rm gal}=52350;$ 
and an  $\mstar>10^{11}\msun$ sample with $z_{\rm max}=0.1$ and $N_{\rm gal}=33578.$ We follow standard practice \citep[e.g.,][]{zehavi_etal11} and throw out all galaxies with $z<z_{\rm min}=0.02;$ we also throw out galaxies with redshift $z \geq z_{\rm max}=0.1$ even in cases where a volume-limited sample would be attainable out to higher redshift.

@@

In Figure~\ref{fig:rvir_only_clustering_absolute}, we present new measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj(\rproj).$ As described in \S\ref{sec:data}, we measure $\wproj(\rproj)$ separately for large and small subsamples for four different $\mstar$ thresholds: $\log\mstar/\msun\geq 9.75, 10.25, 10.75, 11.$ 
%$\mstar\geq10^{9.75}\msun; \mstar\geq10^{10.25}\msun; \mstar\geq10^{10.75}\msun; \mstar\geq10^{11}\msun.$ 
For each threshold, we split the galaxies into ``large" and ``small" subsamples, as described in \S\ref{subsec:sizedef}. As shown in Figure \ref{fig:sizedefinition}, our size-based samples  have similar stellar mass functions. Red points with jackknife-estimated error bars show SDSS measurements of $\wproj(\rproj)$ for samples of small galaxies, while blue points show the measured correlation functions for samples of large galaxies. Solid curves show $\wproj$ as predicted for these subsamples by the $\rvir-$based model of galaxy sizes described in \S\ref{subsubsec:rvirmodel}.
